Isomorphic Interpreters from Logically Reversible Abstract Machines

### 2012-05-29 iso-int/rc-iso-int.tex
fixes

Our translation apply to machines presented as small-step operational
semantics, i.e. machines that are step-wise rewrites of tuples of
algebraic datatypes, wherein each rewrite step must be logically
reversible. The formal criterion logical reversibility in this setting
are captured in Abramsky's presentation of \emph{bi-orthogonal
  automata} \cite{abramsky2005structural} and may be summarized as:
\begin{enumerate}
\item
  Machines must have distinguishable start and stop states. There may
  be more than one valid start state and more than one valid stop
  state.
\item Each valid machine state must match a unique pattern on the
  left-hand-side and right-hand-side of the `{{|-->}}' rewrite.
\item Every reduction step must be computable (in {{langRevT}}) and
  must be logically reversible -- i.e. it must be possible to reduce
  from right to left.
\end{enumerate}

>>>>

Our translation apply to machines presented as small-step operational
semantics, i.e. machines that are step-wise rewrites of tuples of
algebraic datatypes, wherein each rewrite step must be logically
reversible. The formal criterion logical reversibility in this setting
are captured in Abramsky's presentation of \emph{bi-orthogonal
  automata} \cite{abramsky2005structural} (see Sec. 2) and may be
summarized as:
\begin{enumerate}
\item
  Machines must have distinguishable start and stop states. There may
  be more than one valid start state and more than one valid stop
  state.
\item Each valid machine state must match a unique pattern on the
  left-hand-side and right-hand-side of the `{{|-->}}' rewrite.
\item Every reduction step must be computable (in {{langRevT}}) and
  must be logically reversible -- i.e. it must be possible to reduce
  from right to left.
\end{enumerate}
